
\Chapter{Bibliography}

\section{Printed Works}
\begin{itemize}
	\item Silberschatz, A., \& Galvin, P.B., \& Gagne, G. (2010).
   Operating System Concepts with Java: John Wiley \& Sons. Inc.
   \item Winn, J., \& Bright, T., \& Jensen, C.G., \& Teng, C. (2013). Utilising game server technology on fully distributed architectures for collaborative multi-user CAx applications: Taylor \& Francis Group.
   \item Vogel, O., \& Arnold, I., \& Chughtai, A., \& Kehrer, T. (2011). Software Architecture: Springer
\end{itemize}

\subsection {Online References}
\begin{itemize}
	\item Microsoft 1. Remotable and Nonremotable Objects. Retrieved 16/12/2015, from https://msdn.microsoft.com/library/h8f0y3fc.aspx
	\item Microsoft 2. .NET Framework Remoting Architecture. Retrieved 16/12/2015, from https://msdn.microsoft.com/en-us/library/2e7z38xb.aspx
	\item Microsoft 3. What Is Windows Communication Foundation. Retrieved 16/12/2015, from https://msdn.microsoft.com/en-us/library/ms731082.aspx
	\item Microsoft 4. How to: Create a Duplex Contract. Retrieved 16/12/2015, from https://msdn.microsoft.com/en-us/library/ms731184(v=vs.110).aspx
	\item Microsoft 5. NetNamedPipeBinding Class. Retrieved 16/12/2015, https://msdn.microsoft.com/en-us/library/system.servicemodel.netnamedpipebinding.aspx
	\item Microsoft 6. ThreadPool Class. Retrieved 16/12/2015, https://msdn.microsoft.com/en-us/library/system.threading.threadpool.aspx
	\item Microsoft 7. Dispatcher Class. Retrieved 16/12/2015, https://msdn.microsoft.com/en-us/library/system.windows.threading.dispatcher.aspx
	\item Microsoft 8. Concurrency Management. Retrieved 16/12/2015, https://msdn.microsoft.com/en-us/library/orm-9780596521301-02-08.aspx
	\item Microsoft 9. Types Supported by the Data Contract Serializer. Retrieved 16/12/2015, https://msdn.microsoft.com/en-us/library/ms731923.aspx
	\item Microsoft 10. Using Data Contracts. Retrieved 16/12/2015, https://msdn.microsoft.com/en-us/library/ms733127.aspx
	\item Microsoft 11. Chapter 7: Message and Transport Security. Retrieved 16/12/2015, https://msdn.microsoft.com/en-us/library/ff648863.aspx
	\item Microsoft 12. Building Secure ASP.NET Applications: Authentication, Authorization, and Secure Communication. Retrieved 16/12/2015, https://msdn.microsoft.com/en-us/library/ff649205.aspx
  \item srp.pdf, Retrieved 02/2002, Robert C. Martin:   http://www.objectmentor.com/resources/articles/srp.pdf
  \item ocp.pdf, 01/1996, Robert C. Martin:   http://www.objectmentor.com/resources/articles/ocp.pdf
  \item Principles_and_Patterns.pdf, 01/2000, Robert C. Martin: http://www.objectmentor.com/resources/articles/Principles_and_Patterns.pdf
\end{itemize}
