
\section{Project Introduction}

	This semester’s project definition was more open than the last
	 two semester projects. We only had to make a distributed system.
	  So we were free choose a topic, as long as it included a client,
		 a server and a database, which were all connected to make an application.
	\\
	\\
	The project handbook actually gave a case where we could develop
	 a system that would help newly started firms make their way into
	  China’s market for production. We decided that we wanted to
		make something else, so we started brainstorming about what
		 each of us wanted to make, then we all came to the agreement
		  of making a game. After that we brainstormed again, this time
			 about what kind of game we wanted to make. It ended up with
			  the classic board game “Battleship” that we would make into
				 a digital version called “Shipwars”. The game fit the criteria
				 perfectly for the requirements we needed. It could have a client
				 that connects to a server that also have a connection to a database
				  where user data is stored. The game would also fulfil our courses
					requirements on this semester project with things like encryption on
					 user data and a market analysis for the cross culture
					  management course. With this game we would eliminate
						the need for being together in the same room when playing, and
						 instead open the possibility to play against people across
						 the globe.
	\\
When we agreed upon the game and its topic, we had to write a project
formulation, and decided to write about the background of board games.
	\\
	\subsection{Project Formulation}

	As board games are rooted in the physical world, board games are limited
	 to the people who can play against each other locally. In order for
	 physical board games to connect a larger player-base that can play anywhere
	  anytime, the Internet may be necessary in order to make it available
		 worldwide. This creates certain problems and here are the ones the
		  group will focus on solving:
	\begin{itemize}
		\item How to digitize a board game?
		\item How to connect multiple people via the Internet?
		\item How to differentiate between the players?
	\end{itemize}
