
\chapter{Tools}

This chapter will go through all the software
used in the project.

\section{Development tools}

These are the software used directly for developing
 the software

\subsection{Git}

Git is a widely used version control system,
 used by project groups to collaborate as a
  team. When used it creates a repository,
  which makes a history over the changes to
  make it possible to rewind to an earlier
  stage. This was used as the version control
  system for the project.
\subsection{Github}

Github is a git server hosting service. It
 makes a server host a git repository available
 for a team to work on. Most of the hosted
 projects are made available to the public
 as an open source project for others to
  explore and give feedback on. This was used
as the host service for our git repository.

\subsection{Visual Studio}

Visual Studio is one of the most used IDE’s for
 programing a broad range of programming
languages. It was used in this project to
 make all the C# code the final product
  consists of.

\section{Project Management}

These were the software used for managing the task present in the project.

\subsection{Trello}

Trello is a time management website used to create a virtual to-do list. When
 a board is created for the team all the members will be able to contribute to
  the board. It was used as the tool to manage our project’s development cycles
   and divide the different use cases equally between the groups.

\section{Modelling Tool}

This where the tools used to create artifacts for the project.

\subsection{Draw.io}

Draw.io is an online diagram tool able to collaborate with different cloud
 services. The diagrams created here can be shared with the team, allowing
  multiple people to edit

\section{Text Editor}

This were the tool used for creating the documentation created during
 the project.

\subsection{Latex}

 LaTeX is a document modeling language. It allows the user to design
  a document from scratch in plain text. When the document is done it compiles
   the plain text into the finished text file. This is the tool used to create
    the final report as it provides a high level of control over the fine
     details like layout, design and formatting.

\subsection{Google Docs, Google Drive and Microsoft Word}

These were used to make and share documents in the group during the
 development, in a less formal way. Google Docs was our primary text
  editor, where Word was used for assignments.
